Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-26 src/tex/intro.tex
add more citations

Observations of gravitational waves (GWs) from compact binary coalescences (CBCs) is becoming a regular occurrence, 
recently producing catalogs of 90 such detection \cite{GWTC1,gwtc2,GWTC3}. With this growing catalog size, we are steadily approaching a more complete  
understanding of the population properties CBCs, just 7 years after the first observation \cite{o1o2_pop,o3a_pop,o3b_astro_dist}. 
In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration detectors \cite{aLIGO,aVIRGO, KAGRA}, with the increased sensitivities, 
there could be a detection as often as every day \cite{LVK_prospects}. This large influx of incoming data will drastically increase what we can learn by combining all observations
in order to studying the compact object population. The history of these dense objects is imprinted on the properties of the population 
of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitation radiation emitted. The population distibutions 
of merging compact objects inferred from gravitational-wave observations has been shown to be parituclar useful in order to, measure cosmological parameters \citep{Farr_2019HUB}, 
constrain modified gravitational wave propagation, constrain a running Planck mass, look for evidence of ultralight bosons through superradiance, 
constrain stellar nuclear reaction rates \cite{Farmer_2020}, look for primordial black holes \cite{Ng_2021}, and constrain the neutron star equation of state \bruce{Cite all points}. 
Through a better understanding of the mass, spin, and redshift distributions of compact binaries that will come with the increased catalog size, 
one can probe a wide range of different physical phenoma with even greater fidelity.

>>>>

Observations of gravitational waves (GWs) from compact binary coalescences (CBCs) is becoming a regular occurrence, 
recently producing catalogs of 90 such detection \cite{GWTC1,gwtc2,GWTC3}. With this growing catalog size, we are steadily approaching a more complete  
understanding of the population properties CBCs, just 7 years after the first observation \cite{o1o2_pop,o3a_pop,o3b_astro_dist}. 
In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration detectors \citep{aLIGO,aVIRGO}, with the increased sensitivities, 
there could be a detection as often as every day \cite{LVK_prospects}. This large influx of incoming data will drastically increase what we can learn by combining all observations
in order to studying the compact object population. The history of these dense objects is imprinted on the properties of the population 
of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitation radiation emitted. The population distibutions 
of merging compact objects inferred from gravitational-wave observations has been shown to be parituclar useful in order to, measure cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, 
constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2}, constrain a running Planck mass \citep{Lagos_runningPlanckMass}, look for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,Ng_BosonGWTC2_2021}, 
constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, and constrain the neutron star equation of state \citep{Golomb_EOS}. 
Through a better understanding of the mass, spin, and redshift distributions of compact binaries that will come with the increased catalog size, 
one can probe a wide range of different physical phenoma with even greater fidelity.
